---
author: "Callin Switzer, Stat110, Hw2 #3(c)"
date: "September 16, 2014"
output: pdf_document
---
# 3(c)
*Here is a graph, showing the two functions f(p) = 3p (dotted line), and f(p) = 3p - 3p^2 + p^3 (solid line).*
*f(p)=3p represents what your chances of winning would be if you tripled your chances by purchasing three tickets*

*f(p) = 3p - 3p^2 + p^3 represents the actual chances of winning when you buy three tickets, over the range of possible p (that is, 0 to 1).* 

*You can also  see that for small values of p, the increase is nearly 3p*

```{r}
# numbers from 0 to 1
nums <- (1:1000)/1000

# f(p) = 3p
three <- nums*3

# f(p) = 3p - 3p^2 + p^3
under <- 1 - (1-nums)^3

# plot and add a line
plot(three~nums, type = "l", lty = 3, xlab = "p", ylab = "f(p)", ylim = c(0,1))
lines(under~nums, type = "l", lty=1)
legend("bottomright", legend = c("f(p) = 3p", "f(p) = 3p - 3p^2 + p^3"), lty = c(3,1))
```


```{r}
dbinom(x = 14, size = 20, prob = (2/3))

library(MASS)
(choose(20,14) *(0.75)^14*(0.25)^6)

?pbinom()

dbinom(x = 14, 20, 0.5)

(0.1686093 * (2/3))/ ((1/3) + 0.03696442 * (1/3))

```