---
title: "Hw5, Q1b"
author: "Callin Switzer"
date: "October 5, 2014"
output: pdf_document
---

```{r echo = T, message = F}
#install.packages("actuar")
library(actuar)
library(plyr)
require(ggplot2)
theoretical <- data.frame( dat = rpareto1(1000000, shape = 10, min = 1))
theoretical$da <-  "Theoretical"
calculated <- data.frame(dat =  (1-runif(1000000))^(-1/10))
calculated$da <- "Calculated"
thcalc <- rbind(theoretical, calculated)

```
I checked that my method worked via simulation.  I simulated large sample from a pareto distribution -- in R, I used rpareto1(1000000, shape = a, min= 1). Next, I simulated a large sample from my calculation using a uniform distribution -- that is, (1-runif(1000000))^(-1/a).  I plotted the two distributions below.

```{r, echo = T}
ggplot(thcalc, aes(dat)) + 
     geom_histogram(alpha = 0.5, aes(y = ..density.., fill = da), 
                    position = 'identity', binwidth = 0.05, color = 
                         "black") + 
     xlim(1,2) +
     ylim(0, 6) + 
     facet_grid(. ~ da)+
     labs(x = "Value", title = "Overlapping Histogram") +
     theme_bw() +
     theme(legend.background = element_rect(colour = "black"),
          plot.background = element_blank() ,
          panel.grid.major = element_blank() ,
          panel.grid.minor = element_blank() ,
          panel.border = element_blank(),
          axis.line = element_line(color = 'black')) +
     scale_fill_manual(name = "Histogram", values = c("white", "grey40")) 
```

To convince myself that they were the same, I plotted them over the top of one another, and outlined each bar in black.  If there was a noticeable difference, I should be able to see a gap between the white and grey on these distributions.  However, I see none.  This directly checks that my method works for generating pareto rvs.

```{r, echo = T}
ggplot(thcalc, aes(dat, fill = da)) + 
     geom_histogram(alpha = 0.5, aes(y = ..density..), 
                    position = 'identity', binwidth = 0.05, color = 
                         "black") + 
     xlim(1,2) +
     ylim(0, 6) + 
     labs(x = "Value", title = "Overlapping Histogram") +
     theme_bw() +
     theme(legend.background = element_rect(colour = "black"),
          plot.background = element_blank() ,
          panel.grid.major = element_blank() ,
          panel.grid.minor = element_blank() ,
          panel.border = element_blank(),
          axis.line = element_line(color = 'black')) +
     scale_fill_manual(name = "Histogram", values = c("white", "grey40"))  

```
