---
title: "Hw5, Q1b"
author: "Callin Switzer"
date: "October 5, 2014"
output: pdf_document
---

```{r echo = T, message = F}
#install.packages("actuar")
library(actuar)
library(plyr)
require(ggplot2)
theoretical <- data.frame( dat = rpareto1(1000000, shape = 10, min = 1))
theoretical$da <-  "Theoretical"
calculated <- data.frame(dat =  (1-runif(1000000))^(-1/10))
calculated$da <- "Calculated"
thcalc <- rbind(theoretical, calculated)

```
I checked that my method worked via simulation.  I simulated large sample from a pareto distribution -- in R, I used rpareto1(1000000, shape = a, min= 1). Next, I simulated a large sample from my calculation using a uniform distribution -- that is, (1-runif(1000000))^(-1/a).  I plotted the two distributions below.  I did this for a variety of a's, and the distributions always looked the same.  The below example has a = 10.

```{r, echo = T, fig.height=3}
ggplot(thcalc, aes(dat)) + 
     geom_histogram(alpha = 0.5, aes(y = ..density.., fill = da), 
                    position = 'identity', binwidth = 0.05, color = 
                         "black") + 
     xlim(1,2) +
     ylim(0, 6) + 
     facet_grid(. ~ da)+
     labs(x = "Value", title = "Overlapping Histogram") +
     theme_bw() +
     theme(legend.background = element_rect(colour = "black"),
          plot.background = element_blank() ,
          panel.grid.major = element_blank() ,
          panel.grid.minor = element_blank() ,
          panel.border = element_blank(),
          axis.line = element_line(color = 'black')) +
     scale_fill_manual(name = "Histogram", values = c("white", "grey40")) 
```

To convince myself that they were the same, I plotted them over the top of one another, and outlined each bar in black.  If there was a noticeable difference, I should be able to see a gap between the white and grey on these distributions.  However, I see none.  This directly checks that my method works for generating pareto rvs.

```{r, echo = T, fig.height=3}
ggplot(thcalc, aes(dat, fill = da)) + 
     geom_histogram(alpha = 0.5, aes(y = ..density..), 
                    position = 'identity', binwidth = 0.05, color = 
                         "black") + 
     xlim(1,2) +
     ylim(0, 6) + 
     labs(x = "Value", title = "Overlapping Histogram") +
     theme_bw() +
     theme(legend.background = element_rect(colour = "black"),
          plot.background = element_blank() ,
          panel.grid.major = element_blank() ,
          panel.grid.minor = element_blank() ,
          panel.border = element_blank(),
          axis.line = element_line(color = 'black')) +
     scale_fill_manual(name = "Histogram", values = c("white", "grey40"))  

```


\newpage

```{r}
ra <- pi * runif(1000000)^2
hist(ra)
mean(ra)
var(ra)
median(ra)


un <- sqrt(ra / pi)
hist(un)
mean(un)

hist(sqrt(runif(10000) / pi))

A <- runif(10000, min = 0, max = pi)
hist (1/2 * 1/(sqrt(pi * A)), breaks = 50)

max(A)
##
po <- rchisq(1000000, df = 2)
hist(po)
mean(po)
median(po)
var(po)
pi/2
```


```{r}
## Q3

x <- seq(0,1, length.out = 1000)
fx <- 2/pi* asin(sqrt(x))
plot(x, fx, type = "l")

foob <- c(5,5,10)
var(foob)
mean(foob)
library(MASS)
fractions((((5-6.6666)^2)*(2) + ((10 - 6.6666)^2))/3)

fractions(25 + 100/9 + 50/9)
```